\Large Classifying Vehicles From Automatic Number \\ Plate Recognition Camera Scans

### 2018-01-29 paper.tex
Ordered bibliography by name, added new input file

\documentclass[twoside,leqno,twocolumn]{article}
\usepackage{ltexpprt}
\usepackage{parskip}

@@

@@

@@

>>>>

\documentclass[twoside,leqno,twocolumn]{article}
\usepackage{ltexpprt}
\usepackage{parskip}
\usepackage[inline]{enumitem}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage[many]{tcolorbox}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{graphicx}

\newcommand{\Tau}{\mathrm{T}}

@@

\input{dataset.tex}

@@

\bibitem{Castillo2010}
Castillo, Enrique, et al. {\em Optimal use of plate-scanning resources for route flow estimation in traffic networks}. IEEE Transactions on Intelligent Transportation Systems 11.2 (2010): 380-391.

@@

\bibitem{ShortestPath?2015}
Zhu, Shanjiang, and David Levinson. {\em Do people use the shortest path? An empirical test of Wardrop’s first principle}. PloS one 10.8 (2015): e0134322.
